Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-08 MUSES_vs_BYOD_solutions.tex
Rewrite a part of Section 3.1. Closes #30

Main services offered by IBM can be divided into three categories: Mobile Enterprise Services, Hosted Mobile Device Security Management, and Enterprise Wireless Networks. However, here we only discuss the former, because it is the only one related to BYOD. Mobile Enterprise Services is offered as an integrated solution for smartphones and tablets as well, but then it is divided in different sub-services that the company has to acquire separately. Some of them are related, to cloud computing. Among them, there is one which is interesting for the scope of this paper, the so-called `hosted vulnerability management'. This sub-service seems to implement one of the most important advantages of the MUSES system, the self-adaptation. IBM performs deep scans over the security incidents data, either by computer forensics analysis, if the incident happened, or by normal data, if the device was enough secure. They claim in their website \footnote{\url{http://www-935.ibm.com/services/us/en/it-services/security-services/vulnerability-management/}} that their tool is able to recognize new vulnerabilities - or threats - with enough accuracy. The main difference with MUSES in this case, is that MUSES includes this feature in the system, without the need of purchasing the service separately and configuring the different parts. Another difference is the fact that IBM software is not open source as MUSES system is. Then, to verify the success of this feature is highly difficult, as they do not present statistics in their website either.

%FERGU: HABLANDO DE LOS PRODUCTOS
IBM also offers some products related to BYOD security. {\em MobileFirst} \footnote{\url{http://www.ibm.com/mobilefirst}} is a set of mobile applications and services, based in big data analytics and cloud computing. It includes several products, such as a framework for app development (MobileFirst Platform), a Platform as a Service (BlueMix) or a threat detection system (Trusteer Rapport). %FERGU: sí, es rApport, no rEpport, no lo cambiéis :P
 However, the most interesting one with respect to this work scope, is {\em MobileFirst Protect}. This product, formerly known as {\em MaaS360} \footnote{\url{http://www.maas360.com/}}, is an MDM (Mobile Device Management) software to secure, monitor, and manage mobile devices. It uses a web portal in order to centralize the security and control policies. This allows the deployment of applications or backups, among other possibilities. However, MobileFirst Protect seems a typical MDM tool, which just applies the existing set of security policies. No further risk and trust analysis is performed, neither is included a refinement of the rules derived from the policies.

>>>>

Main services offered by IBM can be divided into three categories: Mobile Enterprise Services, Hosted Mobile Device Security Management, and Enterprise Wireless Networks. However, here we only discuss the former, because it is the only one related to BYOD. Mobile Enterprise Services is offered as an integrated solution for smartphones and tablets as well, but then it is divided in different sub-services that the company has to acquire separately. Some of them are related, to cloud computing. Among them, there is one which is interesting for the scope of this paper, the so-called `hosted vulnerability management'. This sub-service seems to implement one of the most important advantages of the MUSES system, the self-adaptation. IBM performs deep scans over the security incidents data, either by computer forensics analysis, if the incident happened, or by normal data, if the device was enough secure. They claim in their website \footnote{\url{http://www-935.ibm.com/services/us/en/it-services/security-services/vulnerability-management/}} that their tool is able to recognize new vulnerabilities - or threats - with enough accuracy.

%FERGU: HABLANDO DE LOS PRODUCTOS
The specific IBM products related to BYOD security are included in their {\em MobileFirst} \footnote{\url{http://www.ibm.com/mobilefirst}} suite. MobileFirst is a set of mobile applications and services, based in big data analytics and cloud computing. It includes several products, such as a framework for app development (MobileFirst Platform), a Platform as a Service (BlueMix) or a threat detection system (Trusteer Rapport). %FERGU: sí, es rApport, no rEpport, no lo cambiéis :P
 However, the most interesting one with respect to this work scope, is {\em MobileFirst Protect}. This product, formerly known as {\em MaaS360} \footnote{\url{http://www.maas360.com/}}, is an MDM (Mobile Device Management) software to secure, monitor, and manage mobile devices. It uses a web portal in order to centralize the security and control policies. This allows the deployment of applications or backups, among other possibilities. However, MobileFirst Protect seems a typical MDM tool, which just applies the existing set of security policies. No further risk and trust analysis is performed, neither is included a refinement of the rules derived from the policies.

 The main difference with MUSES in this case, is that MUSES includes this feature in the system, without the need of purchasing the service separately and configuring the different parts. Another difference is the fact that IBM software is not open source as MUSES system is. Then, to verify the success of this feature is highly difficult, as they do not present statistics in their website either.
